SFJ: An implementation of Semantic Featherweight Java

### 2020-04-24 conference/camera ready/paper.tex

\section{Conclusion, Related and Future Work}
\label{sec:conclusion}

>>>>

\section{Code generation}

So far, SFJ only includes the typechecking component of the language. We provide a ``proof'' of the code generation algorithm for areas of future work.

Given the similarity of SFJ to Java, we felt that the usage of the Java Virtual Machine (JVM) \cite{lindholm2013} would be most suitable for code generation by transpiling SFJ programs into JVM bytecode.
This is the approach used by object-oriented languages such as Kotlin amongst others.

The key challenge in implementing code generation compared to other languages is that a single field in SFJ with type $(int\ \textbf{or}\ bool)$ actually represents two JVM fields, one of type $int$ and another of type $bool$, of which only one is inhabited with a value.

Therefore to reduce the amount of alternatives for which we would need to generate code, we first analyse our program and reduce the boolean types by keeping only the alternatives which actually get used in the program.
For example, if the field of type $int\ or\ bool$ only ever gets initialised with a boolean value, we can reduce it and make it a field of a single type $bool$.
Similarly the numerical basic types can also be reduced to their largest type without consequence, such as $int\ \textbf{and not}\ byte$ can be reduced to just $int$ as we have already type checked all literal values passed to such a type.

After reducing the boolean types, we have to expand all boolean types that still remain by considering the result of their set operation.
Staying with the example of a field named $f1$ of type $int\ or\ bool$, we would define in our class two fields $int\_f1$ and $bool\_f1$ with types $int$ and $boolean$ respectively.
In order to initialise these field, we use the constructor overloading capabilities of the JVM to generate an overloaded version for each alternative type.
In each constructor, only the alternative field that matches the type of the parameter in this constructor is initialised with a value and all other alternatives are set to $null$.

For methods, we also use the overloading capabilities of the JVM to define an  overloaded method for each type in the expanded method parameter, all with the same method body.
Depending on which alternative the argument inhabits at run-time, a different method will be dispatched to.

To access the field of an object, we generate code that checks each alternative of the field if it is non-null and includes the rest of the code generation for the expression for each branch. At runtime, only one branch will be true, and this is the branch of generated code which will be executed.

For structural subtyping, we create an new nominal subtype with the same implementation for each structural subtype a type has, so that it is accepted as a proper subtype in the JVM.

Like methods with boolean types, we similarly implement methods with method types by defining an overloaded alternative for each type that implements the specified method.

We have now defined the code generation for each expression in our syntax of terms and for field, constructor and method declarations, so therefore have defined how

\section{Conclusion, Related Work and Future Work}
\label{sec:conclusion}
